LogChunks: A Data Set for Build Log Analysis

### 2020-01-28 msr-paper/paper.tex
Finish review

% TODO remove XD
\usepackage{xcolor}
\newcommand{\secfunc}[1]{{\color{magenta}#1}}
\newcommand{\mention}[1]{{\color{cyan}#1}}
\newcommand{\plan}[1]{{\color{purple}#1}}
\newcommand{\bp}[1]{{\color{violet}#1}}
\newcommand{\draft}[1]{{\color{blue}#1}}
\newcommand{\review}[1]{{\color{black}#1}}
\newcommand{\todo}[1]{{\color{orange}(#1)}}

\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}

@@

While still in their infancy, we believe that having a common dataset
to be able to fairly compare different build log analysis techniques
will advance the research area and ultimately increase our
understanding of CI build failures. In this paper, we present
\emph{LogChunks}, a collection of 797 annotated Travis CI build
logs from 80 GitHub repositories in 29 programming languages. For each
build log, LogChunks contains a manually labeled log part (chunk)
describing why the build failed. We externally validated the data set
with the developers who caused the original build failure.

The width and depth of the \emph{LogChunks} data set are intended to
make it the default benchmark for automated build log analysis
techniques.
\end{abstract}

@@

Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks
  is openly available on Zenodo: \todo{insert zenodo link}} a
collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

\begin{figure*}[tbp]
	\centering
	\includegraphics[width=1.35\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure*}

\section{Creating LogChunks}
This section presents how we gathered the logs and our manual labeling process.
\label{sec:data-collection}

\subsection{Log Collection}
In this section, we describe along the overview in
\Cref{fig:lc-overview} how we created \emph{LogChunks}. All steps are
automatized as Ruby scripts\footnote{Data collection scripts avaliable
  on GitHub: http://tiny.cc/data-collection} and highly configurable.

@@

For \emph{LogChunks}, we queried GHTorrent on 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\paragraph{Build Sampling}
To sample the builds for \emph{LogChunks} we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

\paragraph{Log Sampling}
Travis CI builds comprise a number of jobs that actualize a build
process in different environments. Hence, the outcome from different
jobs might be different. For each build in LogChunks, we download the
first job which has the same state as the overall build.

@@

%For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
%
%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.

In our second validation, we sent out emails to the original
developers whose commits triggered the builds represented in
\emph{LogChunks} and asked them whether the log chunk we labeled
actually describes why the build failed.  This section describes our
survey and discusses our results.

\paragraph{Method}
Using the Travis API, we collected the commit information for each build represented in \emph{LogChunks}.
We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
It included links to the corresponding commits, build overview and log file.
We asked the developers to fill out a short form in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.

@@

\paragraph{Discussion}
We believe that our developer survey highly strengthens the trust in
the validity of the labeled log chunks.  The study received answers
for about 18\% of the data in \emph{LogChunks}.  After manual
correction, 91\% of the received answers indicated our labeled chunks
were accurate.  One possible threat regarding the high number of
correct answers is that, since we show the error message we extracted,
it might be operationally easier for developers to validate it, rather
than search for it in a long log file. To alleviate this problem, we
made it as easy to confirm as to reject an extracted log chunk. We
only ask for more details (the correct log chunk) in a second step.

@@

\begin{table*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  Data & Description & Unit & Example \\
  \midrule
  Log & Relative path to the input build log & Unique Path & \tt{C/php@php-src/failed/529279089.log} \\
  Chunk & Log chunk that describes why the build failed & String & \tt{001+ ** ERROR: process timed out **\newline
001- OK.\newline
========DONE========\newline
FAIL Bug \#60120 (proc\_open hangs)} \\ 
  Keywords & Keywords the authors would use to search for and find the log chunk & List of Strings & \tt{ERROR, FAIL, DIFF} \\ 
  Category & Categorization of the structural representation of the log chunk within the build log & Integer & \tt{0}\\
  \bottomrule
\end{tabularx}
\caption{Exemplary, complete data excerpt from \emph{LogChunks} for a failed build in \tt{php@php-src}.}
\label{tab:data-in-example}
\end{table*}

@@

This section presents the internal structure and data schema of
\emph{LogChunks}. In principle, LogChunks comprises automatically
retrieved logs, as well as manually labeled and cross-validated data.

%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
LogChunks comprises information on 797 build logs, which are organized in folders for each language and repository.
For each repository, \emph{LogChunks} has about 10 \texttt{Examples}. Within a repository folder, there is a folder \todo{foldername} \texttt{} for the general build status (`failed'), which contains the full log files in plain text.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.

The folder \texttt{build-failure-reason} contains the manually labeled
data of \emph{LogChunks}, one XML file for each repository: \\
\texttt{\textless repository\_owner\textgreater @\textless
  repository\_name\textgreater.xml}.  \Cref{tab:data-in-example} gives
an overview of the data within these XML files on the example of one
build from \texttt{php@php-src}. The remainder of this section defines
in more detail the data embedded in the XML files, that is, the
labeled log chunk, search keywords and structural categories.

@@

\paragraph{Search Keywords}
The \texttt{Keywords} contain a list of one to three freely chosen search strings appearing within the \texttt{Chunk} or in the area around it in the build log.
We selected keywords the authors would use to search for the log \texttt{Chunk}, as we found them repeatedly next to failure describing chunks while analyzing about 800 build logs manually.
Some keywords from \emph{LogChunks} are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.

@@

%\section{Applications}
%This section possible use cases for \emph{LogChunks} and outlines how we previously applied it to compare different build log analysis techniques.
\section{Potential Use Cases}

%\subsection{Potential Use Cases}
\emph{LogChunks} can be the basis for a range of further studies:

\paragraph{Benchmarking Build Log Analysis Techniques}
\emph{LogChunks} is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
\emph{LogChunks} can be a benchmark to evaluate other build log analysis techniques.
For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.

@@

\paragraph{Research on Build Logs}
The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.

% \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
% \emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
% Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
% We can also recommend users which search keywords they should use to find why the build failed.
% \todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}

@@

\paragraph{Automatic Processing of Build Results}
\emph{LogChunks} enables researchers to train algorithms that retrieve build failure descriptions from build logs and provide the basis for further automatic on-ward processing of the retrieved log chunks.

@@

% \subsection{Chunk Retrieval Evaluation}
% We created \emph{LogChunks} to evaluate and compare different chunk retrieval techniques for build logs.
% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
% A user provides a small number of examples to describe which text part the program should extract.
% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
% Lastly, we investigated searching for keywords that are associated with the given user examples.

@@

\section{Related Data Sets}
\label{sec:related-data-sets}
This section presents existing data sets of CI build logs and how
\emph{LogChunks} differs from them.

\subsection{TravisTorrent}
\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
range of metadata about Travis CI builds\@.  It combines data
accessible through the public Travis CI and GitHub APIs and through
GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
metadata are the failing test cases. However, TravisTorrent obtained
these through a manually developed parser, which only supports
specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
many of the failing tests are at least incomplete and lack
validation. By contrast, \emph{LogChunks} provides manually labeled
and two-fold cross-validated data of why builds failed, not only for
failing tests like TravisTorrent, but for all possible build-failing
errors.

\subsection{LogHub}
\emph{LogHub}~\cite{zhu2019tools} is a collection of a wide range of system log data sets.
It is the basis for various studies that compare different approaches to parse unstructured system log messages into structured data for further analysis. \emph{LogChunks} is situated in a different area, build log analysis, which tend to be semi-structured, and could play a similar role to \emph{LogHub} in its area: 
empower research with a benchmark to compare different build log analysis techniques.

% \subsection{Travis CI Build Log Data Set}
% \todo{I would remove this as it is not really related because it does not contain labels?}
% Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
% They selected Maven repositories that included the Checkstyle plugin.
% Their data set only provides the plain build logs, whereas \emph{LogChunks} additionally provides manually labeled data about the chunk describing why a build failed.

\section{Future Extensions to LogChunks}

In this section, we describe \emph{LogChunk}'s current limitations and future improvements and extensions we are planning.

\paragraph{Chunk as One Consecutive Substring}
The manually labeled \texttt{Chunk} contains only one continuous substring of the log text.
The reason a build failed could be described at multiple locations within the log.
We propose to extend \emph{LogChunks} to contain multiple substrings of the log text.

\paragraph{Include More Repositories and Logs}
\emph{LogChunks} encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
%This stems from the high effort necessary for the manual data labeling process.
Including more logs and repositories into \emph{LogChunks} will strengthen it as a benchmark to compare build log analysis techniques.

@@

\paragraph{Other Targeted Information Chunks}
Build log analysis is not limited to retrieving the chunk describing why a build failed.
\emph{LogChunks} can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.

\paragraph{Validation of Search Keywords}
The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing around 800 build logs.
Next, we propose to evaluate whether these keywords would also be used by developers to find the log chunk describing why a build failed.

\section{Summary}
\label{sec:conclusion}
In this paper, we introduce \emph{LogChunks}, a cross-validated data
set encompassing 797 build logs from 80 projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build
failed and provide keywords a developer would use to search for the
log chunk as well as a categorization of the log chunks according to
their format within the log. \emph{LogChunks} advances the research
field of build log analysis by introducing a benchmark to rigorously
examine research contributions~\cite{sim2003using} and opening various
research possibilites that previously required tedious manual
classification.

>>>>

\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}
\usepackage{xspace}
% TODO remove XD
\usepackage{xcolor}

\newcommand{\secfunc}[1]{{\color{magenta}#1}}
\newcommand{\mention}[1]{{\color{cyan}#1}}
\newcommand{\plan}[1]{{\color{purple}#1}}
\newcommand{\bp}[1]{{\color{violet}#1}}
\newcommand{\draft}[1]{{\color{blue}#1}}
\newcommand{\review}[1]{{\color{black}#1}}
\newcommand{\todo}[1]{{\color{orange}(#1)}}
\newcommand{\logchunks}{\emph{LogChunks}\xspace}

@@

We believe that having a common dataset to be able to fairly compare
different build log analysis techniques will advance the research
area. It will ultimately increase our understanding of CI build
failures. In this paper, we present \logchunks, a collection of 797
annotated Travis CI build logs from 80 GitHub repositories in 29
programming languages. For each build log, \logchunks contains a
manually labeled log part (chunk) describing why the build failed. We
externally validated the data set with the developers who caused the
original build failure.

The width and depth of the \logchunks data set are intended to
make it the default benchmark for automated build log analysis
techniques.
\end{abstract}

@@

Thus, in this paper, we present \logchunks,\footnote{\logchunks
  is openly available on Zenodo: \todo{insert zenodo link}} a
collection of 797 Travis CI build logs from 80 highly popular GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

\begin{figure*}[tbp]
	\centering
	\includegraphics[width=1.35\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \logchunks}
	\label{fig:lc-overview}
\end{figure*}

\section{Creating \logchunks}
This section presents how we gathered the logs and our manual labeling process.
\label{sec:data-collection}

\subsection{Log Collection}
In this section, we describe along the overview in
\Cref{fig:lc-overview} how we created \logchunks. All steps are
automatized as Ruby scripts\footnote{Data collection scripts avaliable
  on GitHub: http://tiny.cc/data-collection} and highly configurable.

@@

For \logchunks, we queried GHTorrent on 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\paragraph{Build Sampling}
To sample the builds for \logchunks we check up to 1,000 builds per repository and keep ten of the status \emph{failed}~\cite{travis2009buildstatus}.
%A Travis CI build is marked as \emph{failed} when it faults in the \texttt{script} section of the build configuration defined by the user.

\paragraph{Log Sampling}
Travis CI builds comprise a number of jobs that actualize a build
process in different environments. Hence, the outcome from different
jobs might be different. For each build in \logchunks, we download the
first job which has the same state as the overall build.

@@

%For \logchunks we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
%As we are not involved in the development of any of the projects within our data set we could only rely on our previous experience with various build logs and systems.
%We only took the logs into account and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.
%
%The person who probably knows best why a build failed is the one committing the changes which triggered the build.
%If the build was e.g.\ part of a pull request then developer likely inspected the failed build and tried to fix the build so the pull request can be accepted.

In our second validation, we sent out emails to the original
developers whose commits triggered the builds represented in
\logchunks and asked them whether the log chunk we labeled
actually describes why the build failed.  This section describes our
survey and discusses our results.

\paragraph{Method}
Using the Travis API, we collected the commit information for each build represented in \logchunks.
We grouped all commits triggered by one developer and sent out an email to them. %, asking whether the log part selected during our labeling was indeed describing the reason the build failed.
%Figure~\ref{fig:dev-mail} shows one of the mails sent out.
It included links to the corresponding commits, build overview and log file.
We asked the developers to fill out a short form in case our extraction was not correct.
%Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey, we asked the developer to paste in the log part actually describing the failure reason or describe in their own words why our original extraction was incorrect.

@@

\paragraph{Discussion}
We believe that our developer survey highly strengthens the trust in
the validity of the labeled log chunks.  The study received answers
for about 18\% of the data in \logchunks.  After manual
correction, 91\% of the received answers indicated our labeled chunks
were accurate.  One possible threat regarding the high number of
correct answers is that, since we show the error message we extracted,
it might be operationally easier for developers to validate it, rather
than search for it in a long log file. To alleviate this problem, we
made it as easy to confirm as to reject an extracted log chunk. We
only ask for more details (the correct log chunk) in a second step.

@@

\begin{table*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  Data & Description & Unit & Example \\
  \midrule
  Log & Relative path to the input build log & Unique Path & \tt{C/php@php-src/failed/529279089.log} \\
  Chunk & Log chunk that describes why the build failed & String & \tt{001+ ** ERROR: process timed out **\newline
001- OK.\newline
========DONE========\newline
FAIL Bug \#60120 (proc\_open hangs)} \\ 
  Keywords & Keywords the authors would use to search for and find the log chunk & List of Strings & \tt{ERROR, FAIL, DIFF} \\ 
  Category & Categorization of the structural representation of the log chunk within the build log & Integer & \tt{0}\\
  \bottomrule
\end{tabularx}
\caption{Exemplary, complete data excerpt from \logchunks for a failed build in \tt{php@php-src}.}
\label{tab:data-in-example}
\end{table*}

@@

This section presents the internal structure and data schema of
\logchunks. In principle, \logchunks comprises automatically
retrieved logs, as well as manually labeled and cross-validated data.

%We give a description of the manually labeled data.
%\logchunks has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \logchunks.
\logchunks comprises information on 797 build logs, which are organized in folders for each language and repository.
For each repository, \logchunks has about 10 \texttt{Examples}. Within a repository folder, there is a folder \todo{foldername} \texttt{} for the general build status (`failed'), which contains the full log files in plain text.
% the logs are separated according to build status.
%Currently, \logchunks only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.

The folder \texttt{build-failure-reason} contains the manually labeled
data of \logchunks, one XML file for each repository: \\
\texttt{\textless repository\_owner\textgreater @\textless
  repository\_name\textgreater.xml}.  \Cref{tab:data-in-example} gives
an overview of the data within these XML files on the example of one
build from \texttt{php@php-src}. The remainder of this section defines
in more detail the data embedded in the XML files, that is, the
labeled log chunk, search keywords and structural categories.

@@

\paragraph{Search Keywords}
The \texttt{Keywords} contain a list of one to three freely chosen search strings appearing within the \texttt{Chunk} or in the area around it in the build log.
We selected keywords the authors would use to search for the log \texttt{Chunk}, as we found them repeatedly next to failure describing chunks while analyzing about 800 build logs manually.
Some keywords from \logchunks are  ``\texttt{Error}'', ``\texttt{=DIFF=}'', ``\texttt{ERR!}'', or the keywords shown in \Cref{tab:data-in-example}.

@@

%\section{Applications}
%This section possible use cases for \logchunks and outlines how we previously applied it to compare different build log analysis techniques.
\section{Potential Use Cases}

%\subsection{Potential Use Cases}
\logchunks can be the basis for a range of further studies:

\paragraph{Benchmarking Build Log Analysis Techniques}
\logchunks is a spin-off from research in which we compared three different log chunk retrieval techniques protypically. %\todo{cite journal paper (or preprint?)}.
\logchunks can be a benchmark to evaluate other build log analysis techniques.
For example, we can use the data set to investigate how reliably the diff-based approach of Amar et al.~\cite{amar2019mining} retrieves a build failure reason.

@@

\paragraph{Research on Build Logs}
The data from \logchunks can support research around the topic of build logs such as how developers use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.

% \paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
% \logchunks provides keywords that the authors would use to search for the chunk describing why the build failed.
% Analyzing these can help us understand how users process build logs and which keywords a tool should use to mark an error description.
% We can also recommend users which search keywords they should use to find why the build failed.
% \todo{Isn't this pretty simple and not really worth a research paper? If it is too trivial, we should probably not mention it here.}

@@

\paragraph{Automatic Processing of Build Results}
\logchunks enables researchers to train algorithms that retrieve build failure descriptions from build logs. It can provide the basis for further automatic on-ward processing of the retrieved log chunks.

@@

% \subsection{Chunk Retrieval Evaluation}
% We created \logchunks to evaluate and compare different chunk retrieval techniques for build logs.
% The first technique is based on synthesizing programs from examples using the Microsoft PROSE library.
% A user provides a small number of examples to describe which text part the program should extract.
% PROSE then synthesizes a program of regular expressions that is consistent with these examples.
% We compared this extraction technique to a text similarity approach, which selects the lines of a build log which are most similar to the ones in the given user examples.
% Lastly, we investigated searching for keywords that are associated with the given user examples.

@@

\section{Related Data Sets}
\label{sec:related-data-sets}
This section presents existing data sets of CI build logs and how
\logchunks differs from them.

\subsection{TravisTorrent}
\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
range of metadata about Travis CI builds\@.  It combines data
accessible through the public Travis CI and GitHub APIs and through
GHTorrent~\cite{gousios2013ghtorrent}. Similar to \logchunks, among the
metadata are the failing test cases. However, TravisTorrent obtained
these through a manually developed parser, which only supports
specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
many of the failing tests are at least incomplete and lack
validation. By contrast, \logchunks provides manually labeled
and two-fold cross-validated data of why builds failed, not only for
failing tests like TravisTorrent, but for all possible build-failing
errors.

\subsection{LogHub}
\emph{LogHub}~\cite{zhu2019tools} is a collection of a wide range of system log data sets.
It is the basis for various studies that compare different approaches to parse unstructured system log messages into structured data for further analysis. \logchunks is situated in a different area, build log analysis, which tend to be semi-structured, and could play a similar role to \emph{LogHub} in its area: 
empower research with a benchmark to compare different build log analysis techniques.

% \subsection{Travis CI Build Log Data Set}
% \todo{I would remove this as it is not really related because it does not contain labels?}
% Loriot et al.~\cite{loriot2019dataset, loriot2019styler} collected Travis CI build logs from 130 GitHub repositories to analyze their use of the Checkstyle plugin.
% They selected Maven repositories that included the Checkstyle plugin.
% Their data set only provides the plain build logs, whereas \logchunks additionally provides manually labeled data about the chunk describing why a build failed.

\section{Future Extensions to \logchunks}

In this section, we describe current limitations and future improvements of \logchunks and extensions we are planning.

\paragraph{Chunk as One Consecutive Substring}
The manually labeled \texttt{Chunk} contains only one continuous substring of the log text.
The reason a build failed could be described at multiple locations within the log.
We propose to extend \logchunks to contain multiple substrings of the log text.

\paragraph{Include More Repositories and Logs}
\logchunks encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
%This stems from the high effort necessary for the manual data labeling process.
Including more logs and repositories into \logchunks will strengthen it as a benchmark to compare build log analysis techniques.

@@

\paragraph{Other Targeted Information Chunks}
Build log analysis is not limited to retrieving the chunk describing why a build failed.
\logchunks can be extended with labels for all information that is contained in the build log, such as descriptions of warnings, build infrastructure and more.

\paragraph{Validation of Search Keywords}
The keywords \logchunks provides are based on the experience of the authors gained from analyzing around 800 build logs.
Next, we propose to evaluate whether these keywords would also be used by developers to find the log chunk describing why a build failed.

\section{Summary}
\label{sec:conclusion}
In this paper, we introduce \logchunks, a cross-validated data
set encompassing 797 build logs from 80 projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build
failed and provide keywords a developer would use to search for the
log chunk as well as a categorization of the log chunks according to
their format within the log. \logchunks advances the research
field of build log analysis by introducing a benchmark to rigorously
examine research contributions~\cite{sim2003using} and opening various
research possibilites that previously required tedious manual
classification.
